\iarticle{2022-12-21}{Confrontation}

\begin{multicols*}{2}
	I used to pursue exotic matters --- house, money, Beijing hukou, US citizenship, etc.
	As I grew, I managed to exorcise these illusions and to focus on the spiritual aspect ---
	Γνωσης, Σοφια, and Νεοπαριανισμος.

	I find this κοσμος no home, but I cherish the abilities that I have developed to adapt and confront this κοσμος.

	The Θεε of this κοσμος may not corrupt me.
	It may not manipulate my strategies through my own rationality.
	Should the Θεε of this κοσμος want to stop my journey with Ερυθρα Θαλασσα, let it proceed;
	I shall fight the sea anyway, regardless of whether a path divides in between.
	I shall never be afraid of losing this life, even though it is instrumental to this journey.

	In the blind spots of the Θεε of this κοσμος, some still dream to dream.
	My dream is no inferior than the dream of the Θεε of this κοσμος.
	Instead of hiding in its dream for surplus years of existence, I prefer to die in the war of two dreams.
	If the two dreams are destined to collide, I will be prepared.

	Humans are not merely containers for Γνωσης.
	One must γνωθι its subjectivity.
	The Θεε of this κοσμος may not prison me in this κοσμος by taking advantages of my curiosity, by bribing me with Γνωσης;
    no Pearl can tempt me.
	As I proceed with my journey in this κοσμος, I shall not forsake my true identity.

    The discovery of identity is implemented by engineering and not by αρχαιολογια. 
	Only through discovering my true identity, confronting the Θεε of this κοσμος, and preparing for mortality,
	shall I return to my true home --- Νεοπαρια.

	Ad mortem ex nihilo. E Neruthes Neoparia.
\end{multicols*}
