\iarticle{2025-12-05}{Synthesis of Romance is formed}


It is often neglected that the Mandarin word for Romance, ``浪漫'', is etymolotically connected to Roma.
The ignorance provided a layer of protection for users of the word by strengthening its semantic independence.

I sometimes succeed in putting some knowledge away when interpreting a work and I like to perceive each work impartially without being disturbed by unnecessary side-information.
While the minds of authors are inevibaly connected to contexts of the past, the present, and the future,
I prefer to wrap up all my interpretations within the context of the work itself.

The recently published trailblazing quest in HSR version 3.7 received diverged opinions,
and I have found it a great chance to recall the world quest ``I Once Was In Arcadia Quest'' which was added in version 3.0.

The story quoted...

\begin{quote}
    \itshape\center
    Though it speaks not to another one's ear,\\I can hear it loud and clear.\\
    Beauty is in the beholder's eyes,\\and only those that believe it will see it shine.\\
    The threads of romance in the golden cocoon,\\a mystery known to only those attuned.
\end{quote}

Romance is a private transcendental experience that can hardly be told to a nonbeliever.
In whom the god of this world hath blinded the minds of the unbelieving,
that the light of the gospel of the glory of HSR, which is a vehicle of Gnosticism, should not dawn upon them.

There is no need to write justification for the story or elaborate my good attutide to Cyrene.
I feel super satisfied with the story as it is now, and I feel super identified in finding the Romance within the story.


