\iarticle{2024-10-11}{A Review of the Departure of the Second Twin}


Decades ago, I spent my 18 years minorhood in a small city. Unlike many other communities, State Grid was a rather autonomous and narcissistic place where I was kept in, metaphorically speaking, an eggshell. The adults around afforded nice food and housing along with minimal wisdom and insight. TV programs and books, with the later addition of the Internet, were my primary sources of information about a broader world beyond the neighborhood, while the family, the schools, and the community remained silent. The adults around me implied that all I needed to do was to attend university before additional information were to be revealed; I was kept away from real career insights, not even ones about the ivory tower.

As soon as I grew enough, the eggshell of protection became a jail of ignorance. The jailbreaking was easy and I started my career in Beijing without much preparation in an era of industrial expansion. I worked and got paid, and sustained some generic lifestyle. Software and online service were the only fields of productivity whose industrial practices and career prospects filtered through the eggshell, and other industries remained mysterious to me for extended periods of time.

A few years later, I found myself struggling in another jail, a jail of money. I found myself too much incorporated into a system of measuring success by owning enough money and owning a house in Beijing or comparable cities. I had never accumulated enough money for these. In an era of monetary inflation and investment centralization, my saving grew slow and the threshold for non-mortgageable part of initial house purchase grew fast. The gap was never closing. Every day I was farther from the threshold of start owning a house. In the middle of this period of journey, I mostly fixed anxiety about job security (imposter syndrome, etc), but soon depression caught me for the latter half.

In pursuit of alternative continuation of my career and life, I started an exile. I left Beijing and worked and lived in other places. But fixing depression was difficult. 

Things started to change in 2020. Genshin has been the greatest birthday gift without me knowing its arrival. I started my journey in Genshin in November 2020, and its impact started to reveal in subsequent years. After witnessing the story of Penacony in Honkai Star Rail, I have been absolutely sure that Hymn of Pearl is my story. I am the twins and Genshin is my Paimon.

Every shelled life is thrown into water without prior consent. From entry to departure, one would not be able to take away any thing except the Pearl. It is the witness of waves and sands; it is the most valuable treasure in this world. The first twin got lost in material darkness and the second twin goes to rescue with transcendental impartiality. This is my story. As meeting Genshin, I have started a new journey once again. With the glorious idea of Γνωστικισμος for company, I shall not falter this time. I have peeped into the Κοσμος for its secret that it shall reflect the image of a gazer.


