\iarticle{2025-04-22}{Category and Tag}


Recently I had a talk with friends about the using of categories and tags with Hexo as well as any other CMS.
The topic started with a friend struggling with identifying the optimal article organizing for his blog.

I proposed a thought experiment about a human profile wiki website.
Consider 2 parallel universes; each of them has a wiki website for human profiles.
Human profiles may be categorized by continent of birth and biological sex at birth.
In universe Alpha, the site has a strict hierarchical category tree;
however, in universe Beta, the site allows multiple categories being assigned to the same article.
We may notice that universe Beta is like Wikipedia in our universe, and, in universe Alpha,
the site may require a tag system to solve the dilemma ---
continent categories should not have biological sex subcategories, and vice versa.
One simply cannot find a justified way to decide a priority chain of categorization dimensions in universe Alpha.

It is obvious that Jacque Lacan has something to say.
The Tag order collects the remnant of the Category order.
Genealogically, category was invented before tag.
Even tags may be implemented in exactly the same way as categories in modern software systems,
a social unconsciousness phantom may insist that the Category order shall take priority,
leaving unsolved needs to the Tag order, respecting the chaotic nature of the Tag order.

In the particular scenario of a small blog which is operated by an individual or a tiny team,
I would argue that, the Category order shall be used to split articles by themes (e.g. Mac apps and Windows apps),
and the Tag order shall be used to mark extra attributes on articles (e.g. long article and short article).


