\iarticle{2022-12-25}{Requiem for Cold War 1}

\begin{multicols*}{2}
    
It is 2022-12-25 today, a date which symbolizes the death of CCCP.
I have been over 27 years old by the end of year 2022;
the days when I had faith in US beacon theory or CCCP hero theory had far gone.
However, December 25 is still a memorable date --- it symbolizes the end of Cold War 1.
31 years ago, with a coup d'\'etat in Moskva and a change of flag on Kreml, CCCP vanished from existence.

Cold War 1 ended too early to present itself in front of me;
I did not have the chance to set my own eyes and hands on it.
The recollections of the heroic years did remain, though.
From the recollections, I could capture insights and could develop revelations ---
Cold War 1 was the best years in human history.

The confrontation of ideologies forced every major government to help developing countries.
Colonies acquired independence.
US and CCCP invested a lot in the frontier regions (e.g. PRC, ROC, ROK, DPRK, Japan).
Third-world countries received a lot of grants and loans from first-world countries and second-world countries.

The confrontation of ideologies forced every major government to improve domestic governance.
Significant portions of government fiscal expenditures went to science, technology, and education.
CCCP sent people to Earth orbit and US sent people to Moon surface.
The civil rights (e.g. abortion, same-gender marriage) were implemented in some countries or regions.
Workers obtained more social welfare policies in various countries, including those advertised themselves to be capitalist.

They all ended when CCCP was gone.
Without a confrontation of ideologies, the world became corrupted by peace.
War is the ladder to development; yet the warriors abandoned it in selfish pursuits of peace.
How may a peaceful stagnation be better than a war which costs no lives of military personnel?
The collusion for peace was disgusting, and is becoming more disgusting every day.

US is not the beacon of humanity, nor was CCCP the communist heaven; but Cold War 1 was wonderful.
Let Cold War 2 come.
The world requires another century of progression.
I require another Cold War.


\end{multicols*}
