\input{resume/.resume.header.TEX}


\begin{document}
\rmfamily\mdseries


% ===========================
% SECTIONS
% ===========================
\makeinfosection


\begin{minipage}[t]{0.64\textwidth}
	\mysection{CAREER HISTORY}

	\subsecexp{Partner}{Nekostein}{2023/07}{PRESENT}{
		\begin{compactitem}
            \item Led small game development projects.
            \item Published 1 title so far.
		\end{compactitem}\par
	    \myref{Learn more: \href{https://nekostein.com}{nekostein.com}}%
	}

	\subsecexp{Product Principal}{Dimension}{2018/10}{2020/11}{%
		\begin{compactitem}
			\item Managed Maskbook (privacy protection and more).
			\item Managed TesserPG (best mobile OpenPGP app).
			\item Co-chaired agile development workflow with the CTO.
			\item Managed branding for the corporation and the products.
		\end{compactitem}\par
		\myref{Learn more: \href{https://dimension.im}{dimension.im}}%
	}

	\subsecexp{Product Designer}{Zaoshu}{2016/10}{2017/08}{%
		\begin{compactitem}
			\item Pushed the product design iterations with the core service of cloud-based web crawler.
			\item Pushed the introduction of webpage content change-observing features.
			\item Made brainstorm ideas into interaction/visual design.
			\item Made user experience improvements.
		\end{compactitem}%
	}

	\subsecexp{UX Designer}{Jisuanke}{2015/06}{2016/10}{%
		\begin{compactitem}
			\item Maintained interaction design and visual design for the main product,
			interactive online learning of computer science and software development.
			\item Participated branding and marketing.
		\end{compactitem}%
	}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.32\textwidth}
	\raggedright

	\mysection{PROJECTS}

	\subsecproj{Developer}{Pendulum Survivor}{%
		Yet another survivor-like game,
        but you control a pendulum suite, and your enemies are attractors.
		\myref{\href{https://nekostein.com/games/pensur/}{nekoste.in/+pensur}}
	}

	\subsecproj{Developer}{Web Digest}{%
		Automated daily digest from news sources such as Hacker News and Phoronix.
		Made for lazy people, like myself, who hate browsing news websites/apps.\par
		\myref{\href{https://webdigest.pages.dev/}{webdigest.pages.dev}}
	}

	\subsecproj{Product Manager}{Maskbook}{%
		Post encrypted content on social media to avoid exploitation of big data and machine learning.
		Content types made richer.
	}

	\subsecproj{Product Manager}{TesserPG}{%
		OpenPGP app for iOS and Android. Became the most welcomed OpenPGP app on App Store.
		Can interact with other apps as an input method.
	}

\end{minipage}






\vfill
\footnotesize
\fontspec{Seravek}
Copyright {\copyright} 2021-2024 Neruthes
\hfill
Made with \faIcon{heart} and {\LaTeX} on Gentoo Linux




\end{document}




