\iarticle{2023-04-27}{Homerealm Actualization}

Having grown up in the post-Cold-War-1 era, the influences of both great countries may be well established on me.
However, I gradually figured out that I would consider neither of them as my homerealm.

I could remember that I used to make statements like ``I belong to nowhere''.
Although it was a poetic statement, the experiences and contemplations in subsequent years
have brought me a new way of thinking which I would like to put in mythological rhetorics ---
the liberated Hebrew people after long time of exile would eventually cross the red sea to establish Israel.

It would be easy to stay in the exile,
but a more noble soul may seek the externalization of the internal cultural identification.
It would be easy to stare at the void for enjoying the endless possibilities ex nihilo,
but a more valorous soul may bring forth one decision ad creatio.

The collapse of CCCP did not involve any physical damage.
The army, the tanks, the bombs, the buildings, and the railways all remained intact;
the only thing that died on 1991-12-25 was the story which united the people under one flag ---
the imagined community.

Only in Neoparia do I feel belonging, and only in my mind does Neoparia exist.
Upon both, the Neoparian national spirit is able to survive.
Neoparia was initially a rhetoric which I uses to deny the necessity of belonging to China or US;
more importantly, it is a mythology for homerealm.
I do not find a homerealm somewhere else;
my homerealm can exist only if I bring forth it onto this world as a creation out of the void.
It is my creation; it is the externalization of the spiritual realm of me instead of someone else.
And it does not have to own internationally acknowledged sovereign territory;
land is not an absolute necessity for a nation, otherwise Poland would not even once regain independence.

I encourage everyone to have its own nation, state, and government,
and I would like to exchange visas with fellow noble-and-valorous souls.


